---
title: "Logistics Network with Google Maps API"
author: "Tellef Solberg"
date: "20/02/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Context

As more map-data (with longitude and latitude specifications) is becoming increasingly available, companies with logisitcs operations can now to a larger degree utilize this in their planning processes with minimal upfront investment. In this project, I hope to inspire logisitics professionals by providing an example of how maps data from the *Google Maps API* can be applied and visualized in *R*. For more information on how to acquire your API-key and set it up in *R* with the package called *ggmap*, look to:
\
\
https://www.linkedin.com/learning/data-visualization-in-r-with-ggplot2/visualizing-data-with-maps. 
\
\
One of the strengths of using the Google Maps API, is that it can efficienty pull map data in the form of longitude and latitude data points, as well as displaying/visualizaing maps in a convenient way in the RStudio IDE. The packages used throughout the project-report are *ggmap* and *tidyverse*, that both can be used together in map visualizations.
\
\
Lastly, a big thanks to David Kahle for developing and lauching the package to the CRAN-community. Source code for the package can be found at: 
\
https://www.rdocumentation.org/packages/ggmap/versions/3.0.0/source


## 2. Problem

The problem that is being solved in this project is as follows:
\
\
A trucking company in Germany has decided to better visualize their trucking operations for planning purposes. The company is stationed in Cologne, and has currently two milk-run routes; One for nothern customers in the area and one for southern customers in the area. There are three delivery points for the northern customers and four delivery points for the southern customers. 
\
\
Using the Google Maps API, we will:
\
1. Visualize the operational area for the trucks with longitude-and latitude data only
\
2. Visualize the operational area for the trucks in map format
\
3. Introduce some changing conditions and visualize the re-designed routes


## 3. Data Description

(Leave for now)

## 4. Visualizations of the Trucking Network 
\
\

```{r}
require("ggmap")
require("tidyverse")
require("ggthemes")

```

```{r}
register_google(key="AIzaSyBS83qg3lBvZQO9itLvkagw9fPzn6Hw_qQ")
```


#### 1. Operational Area with longitude and latitude

Lon-lat data plots here

#### 2. Operational Area on the map

Lon-lat with map plots here

#### 3. Changing Conditions and Re-design of Routes

(Moving customer, closed road, increased facility costs in Cologne)

## 5. Final Remarks

Final comments and future research

## References






